Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-04-27 main_paper.tex
Add words to Emacs dictionary
Update simulation table with 5000 replications
Also made necessary changes to the text describing this table.

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.018 & 0.066 & 0.069 & 93.1       & 0.240     \\
        & \cctuni    & --0.016 & 0.067 & 0.069 & 92.4       & 0.246     \\
        & \ccttri    & --0.010 & 0.068 & 0.068 & 91.1       & 0.241     \\\\
    2   & \bootuni   & --0.012 & 0.088 & 0.089 & 95.3       & 0.324     \\
        & \cctuni    & --0.010 & 0.087 & 0.088 & 93.8       & 0.350     \\
        & \ccttri    & --0.011 & 0.085 & 0.086 & 93.5       & 0.343     \\\\
    3   & \bootuni   & --0.004 & 0.064 & 0.064 & 96.0       & 0.246     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 94.3       & 0.250     \\
        & \ccttri    & --0.008 & 0.067 & 0.067 & 91.9       & 0.246     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 1500
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.
All of the intervals are reasonably close to their nominal coverage, although
the analytically corrected estimator using the triangular kernel seems to
persistently under-cover by a few percentage points. Our proposed bootstrap
procedure consistently performs well, as it is about a percentage point closer
to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
slightly conservative (96\% coverage) in DGP 3. The final column, ``CI Length,''
indicates that all three of these procedures generate intervals that are
approximately the same length on average.

It is important not to read too much into these simulation results. Where there
are differences between these procedures, they are small enough that randomness
in the simulations is likely a factor in their precise rankings.\footnote{%
  To help address this concern, we are currently running a more extensive set of
  simulations and will update this paper when they are complete.} %
These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.

@@

%  LocalWords:  Calonico Cattaneo Titiunik's Econometrica CCT AMSE CCT's DGP
%  LocalWords:  datasets frolich calonico HTV CIs

>>>>

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
        & \ccttri    & --0.014 & 0.067 & 0.068 & 91.4       & 0.239     \\\\
    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.1       & 0.323     \\
        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\\\
    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

The column ``CI Coverage'' lists the experimental coverage of each interval.
All of the intervals are reasonably close to their nominal coverage, although
the analytically corrected estimators seem to persistently under-cover the true 
ATE (especially the one using triangular kernel). Our proposed bootstrap
procedure consistently performs well, as it is about a percentage point closer
to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
slightly conservative (95.9\% coverage) in DGP 3. The final column, ``CI Length,''
indicates that all three of these procedures generate intervals that are
approximately the same length on average.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.

@@

%  LocalWords:  Calonico Cattaneo Titiunik's Econometrica CCT AMSE CCT's DGP
%  LocalWords:  datasets frolich calonico HTV CIs analytical rdrobust
%  LocalWords:  undersmoothing doParallel foreach doparallel doRNG eq
%  LocalWords:  dorng nonparametrically RMSE ATEs
